\documentclass[answers]{exam}
\renewcommand{\solutiontitle}{\noindent\textbf{Answer:}\par\noindent}
\unframedsolutions

\begin{document}
\pagestyle{empty}
Thanks for your careful review of my manuscript. Below is my response to each point you proposed.

\begin{questions}
\question
About the contribution of the authors, I would suggest to include that all the authors contributed the same in the “Author contribution” section, and not after the affiliations.
\begin{solution}
    As you suggested, I have moved "These authors contributed equally to this work." to the part of "Author Contributions".
\end{solution}

\question In order to follow the journal template, I would suggest to divide the article into sections 1. Introduction, 2. Materials and methods, 3. Results, 4. Discussion, and 5. Conclusion.
\begin{solution}
    Thanks for your suggestion to organize the paper. The current organization
    of the paper loosely follow your suggestions. Therefore, I only make minor changes to the title of sections.
    I have changed the title of the third section to "Models and methods", since we don't need extra materials in this paper.
    Then we use more concrete title "Hermite Polynomials" instead of "Results".
    The title of the next section is also changed to "Experimental validation and discussions" to reflect your suggestion.
\end{solution}
\question Line 20: the word quantitatively is in bold. Please change it
\begin{solution}
    The bold font on the word "quantitatively" is removed.
\end{solution}
\question 
Although the introduction section is very interesting, I would locate “related works” before saying what you are going to do, and I would establish the objective of the study after explaining the pros and cons of previous studies.
\begin{solution}
    I understand that you suggest us
    to put related works before introducing
    our contribution. This is a nice arrangement.
    But the detailed content of related works
    is a little longer. Therefore, in our current approach,
    in the section of "Introduction",
    we only mention some highly related works.
    The whole content is put in a separate section to make the
    reference complete. We think this treatment can make readers easier to grasp our points.
\end{solution}
\end{questions}
I have revised my manuscript to reflect the above changes.

\end{document}
