\documentclass[answers]{exam}
\renewcommand{\solutiontitle}{\noindent\textbf{Answer:}\par\noindent}
\unframedsolutions

\begin{document}
\pagestyle{empty}
Thanks for your careful review of my manuscript. Below is my response to the point you proposed.
\begin{questions}
\question
In my opinion the contribution of this article is small. The authors analyze only the activation function for a single neuron. In order to make the contribution more significant the authors should also investigate the proposed function in a network with more neurons for some practical approximation problem. The scientific contribution and practical applicability of this article is not significant enough for publication.
\begin{solution}
    As you mentioned, we admit that the one-node neural network for regression task studied in this paper is a little restricted study case,
    and our future study direction will just follow your suggestions to consider networks with more neurons, as mentioned in the last sentence of the "Conclusion" section.
    However, our main focus in this paper is to study how much performance gain  non-linearity brings, and to study which kinds of nonlinear activation function is the
    best. To make our intention more clear, we have added the following explanation to the beginning of the "Models and methods" section:

    \textit{
    The one-node neural network is the output layer in a complex neural network for regression task, where
    $\underline{X}$ is the extracted feature vector by previous layers.
    Though our study focuses on this specific network structure, we enlarge the choice of activation term $\sigma$ to find insights
    for the best choice of activation functions.
    }

\end{solution}
\end{questions}
Besides, I have revised my manuscript to reflect the above changes.

\end{document}
